Examining background gene list issue in clusterProfiler - RNA-seq example

### 2024-09-12 analysis/analyse_rnaseq1.Rmd
adding mean to boxplot

par(mar = c(5.1, 8.1, 4.1, 2.1))
library(beeswarm)
boxplot(unsl,horizontal=TRUE,las=1,col=c("pink","lightblue"),cex=0,xlab="no. significant sets FDR<0.05")
beeswarm(unsl,horizontal=TRUE,add=TRUE,col=c("red","blue"),pch=19,cex=0.6)

unsl1 <- unsl+1
boxplot(unsl1,horizontal=TRUE,log="x",las=1,col=c("pink","lightblue"),cex=0,xlab="no. significant sets FDR<0.05*")
beeswarm(unsl1,horizontal=TRUE,add=TRUE,col=c("red","blue"),pch=19,cex=0.6)

@@

png("fig1_ORAsigbox.png")
boxplot(unsl1,horizontal=TRUE,log="x",las=1,col=c("pink","lightblue"),cex=0,xlab="no. significant sets FDR<0.05*")
beeswarm(unsl1,horizontal=TRUE,add=TRUE,col=c("red","blue"),pch=19,cex=0.6)
legend("bottomright", inset=.02, legend=c("corrected","original"),
  fill=c("lightblue","pink"),col=c("blue","red"), horiz=FALSE, cex=1.1)
dev.off()

pdf("fig1_ORAsigbox.pdf",width=7, height=7)
par(mar = c(5.1, 8.1, 4.1, 2.1))
boxplot(unsl1,horizontal=TRUE,log="x",las=1,col=c("pink","lightblue"),cex=0,xlab="no. significant sets FDR<0.05*")
beeswarm(unsl1,horizontal=TRUE,add=TRUE,col=c("red","blue"),pch=19,cex=0.6)
legend("bottomright", inset=.02, legend=c("corrected","original"),
  fill=c("lightblue","pink"),col=c("blue","red"), horiz=FALSE, cex=1.1)
dev.off()

>>>>

par(mar = c(5.1, 8.1, 4.1, 2.1))
library(beeswarm)
boxplot(unsl,horizontal=TRUE,las=1,col=c("pink","lightblue"),cex=0,xlab="no. significant sets FDR<0.05")
beeswarm(unsl,horizontal=TRUE,add=TRUE,col=c("red","blue"),pch=19,cex=0.6)
beeswarm(as.list(colMeans(unsl)),horizontal=TRUE,add=TRUE,col="black",pch="x",cex=1.0)

unsl1 <- unsl+1
boxplot(unsl1,horizontal=TRUE,log="x",las=1,col=c("pink","lightblue"),cex=0,xlab="no. significant sets FDR<0.05*")
beeswarm(unsl1,horizontal=TRUE,add=TRUE,col=c("red","blue"),pch=19,cex=0.6)
beeswarm(as.list(colMeans(unsl1)),horizontal=TRUE,add=TRUE,col="black",pch="x",cex=1.0)

@@

png("fig1_ORAsigbox.png")
boxplot(unsl1,horizontal=TRUE,log="x",las=1,col=c("pink","lightblue"),cex=0,xlab="no. significant sets FDR<0.05*")
beeswarm(unsl1,horizontal=TRUE,add=TRUE,col=c("red","blue"),pch=19,cex=0.6)
beeswarm(as.list(colMeans(unsl1)),horizontal=TRUE,add=TRUE,col="black",pch="x",cex=1.0)
legend("bottomright", inset=.02, legend=c("corrected","original"),
  fill=c("lightblue","pink"),col=c("blue","red"), horiz=FALSE, cex=1.1)
dev.off()

pdf("fig1_ORAsigbox.pdf",width=7, height=7)
par(mar = c(5.1, 8.1, 4.1, 2.1))
boxplot(unsl1,horizontal=TRUE,log="x",las=1,col=c("pink","lightblue"),cex=0,xlab="no. significant sets FDR<0.05*")
beeswarm(unsl1,horizontal=TRUE,add=TRUE,col=c("red","blue"),pch=19,cex=0.6)
beeswarm(as.list(colMeans(unsl1)),horizontal=TRUE,add=TRUE,col="black",pch="x",cex=1.0)
legend("bottomright", inset=.02, legend=c("corrected","original"),
  fill=c("lightblue","pink"),col=c("blue","red"), horiz=FALSE, cex=1.1)
dev.off()
